Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-08-24 analysis/presentation/sim_survey_presentation.Rmd
Start to describe simulation of spatial distribution

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      dev = "png",
                      dpi = 300)
knitr::opts_knit$set(root.dir = "../..")
```

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
# load("analysis/cod_sim_exports/2018-07-13_test/test_output.RData")

@@

- **Dynamic abundance**
- **Spatial aggregation**
- **Survey design**
- **_Objective: build a simulation that emulates reality_**

## Step 1: Simulate abundance

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      fig.height = 4.5, 
                      fig.width = 10)
knitr::opts_knit$set(root.dir = "../..")
```

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-07-13_test/test_output.RData")

@@

- **Dynamic abundance**
- **Spatial aggregation**
- **Survey design**
- **_Objective: build a simulation that emulates reality_**
- **_Roughly based simulation on 3Ps Cod_**

## Simulate abundance

@@

## Simulate abundance

Trend in total abundance

<dev class = "centered"> 
<!-- There is a bug somewhere...had to contain plotly plots in a dev to get it working -->
```{r}
plot_trend(sim) %>% 
  layout(plot_bgcolor = "transparent",
         paper_bgcolor = "transparent",
         margin = list(l = 70, r = 0, t = 0, b = 40, pad = 0),
         font = list(size = 14))
```
</dev>

## Simulate abundance

Trend in abundance at age

<dev class = "centered">
```{r}
plot_surface(sim) %>% 
  layout(plot_bgcolor = "transparent",
         paper_bgcolor = "transparent",
         margin = list(l = 0, r = 0, t = 0, b = 0, pad = 0),
         font = list(size = 14))
```
</dev>

## Simulate spatial aggregation

- Generate a square grid of $s$ locations, resolution $R$ and a depth gradient
- Distribute population through space and add spatial-temporal noise
    - $log(N_{a,y,s}) = log(N_{a,y}) + \eta_{a,y,s}$
    - $\eta_{a,y,s}$ includes parabolic relationship with depth and covariance between ages, years and space
        - $\eta_{a,y,s} = \frac{(d_s - \mu_{d}) ^ 2}{2 \sigma_d^2} + \xi_{a,y,s}$
        - $\xi_{a,y,s}$ is a combination of Matérn covariance and the age-year covariance described in Cadigan [-@Cadigan2016]

## Todo

- Try and figure out the bug that prevents the plotly plots from working in this part of the slideshow (alternate fix to containing it in a device)
- Figure out how to use the Google Font with plotly
- Set-up global layout arguents somehow
